---
title: "RStudio Training Session - Git Hub Version Control in RStudio"
output: html_notebook
---

These are the packages I'm using

```{r}
library(tidyverse)
```

This is how I get my data - "Environment" tab -> "Import Dataset" -> "From TXT (readr)"
Paste in data URL 
Copy code and paste below

```{r}
library(readr)
visits_by_hospital <- read_csv("https://raw.githubusercontent.com/philbowsher/Foundation-of-the-R-Workflow-workshop-2019-09-06/master/Examples/data/visits_by_hospital.csv")
visits_by_hospital
```


Prepping the data

```{r}
newdata <- visits_by_hospital %>%
 filter(!(name %in% c("newport hospital", "rhode island hospital"))) %>%
 filter(!(encounterclass %in% 
 "wellness")) 
 
newdata
```



Visualisation

Addins -> ggplot2_builder

```{r}
ggplot(newdata) +
  aes(x = name, y = n) +
  geom_boxplot(shape = "circle", fill = "#112446") +
  theme_minimal()
```


1. create the token

usethis::create_github_token()

2. Redirect to browser and create the token.

3. Go back to R session and execute:

credentials::set_github_pat(FALSE)

use_git_config(user.name = "alhsu", user.email = "INSERT MY EMAIL HERE")


```{r}
library(usethis)

usethis::create_github_token()

credentials::set_github_pat(FALSE)

use_git_config(user.name = "alhsu", user.email = "INSERT MY EMAIL HERE")

```


I find it useful to first create an issue, then create a branch that contains the issue number in the name, then submit a pull request, and finally delete and forget the branch after the pull request is merged.


